Project draft

### 2022-04-20 Project_draft.Rmd
filter to selected north american countries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

#filter to north american countries american and canada 
#in the years 2007 - 2017
```{r}
america <- deaths_df %>% filter(country == "United States" & year > 1999)
canada <- deaths_df %>% filter(country == "Canada" & year > 1999)
